\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

% Create a version of resumeSubheading without bullets
\newcommand{\resumeCompanyHeading}[4]{
  \vspace{5pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Mohammed Hafeez Ahmed}} & Email: \href{mailto:hafeezhmha.dev@gmail.com}{hafeezhmha.dev@gmail.com}\\
  \href{https://hafeezhmha.vercel.app/}{Portfolio: portfolio/hafeezhmha} & Mobile: +91-8095150412 \\
  \href{https://github.com/hafeezhmha}{Github: github/hafeezhmha} \\
\end{tabular*}

%-----------EDUCATION-----------------
\vspace{-5pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{Python, HTML, CSS, JavaScript, SQL, Bash}
	\resumeSubItem{Frameworks \& Libraries}{PyTorch, Langchain, Scikit-learn, NLTK, SpaCy, Tailwind CSS, Flask, Node.js, OpenCV, Transformers, Diffusion Models (Flux, Wan 2.1)}
	\resumeSubItem{Tools \& Technologies}{Git, Anaconda, Jupyter Notebook, Google Colab, Docker, QGIS, ComfyUI, Replicate, Cog, Hugging Face}
	\resumeSubItem{AI \& ML}{Computer Vision, Large Language Models (LLMs), OCR, NLP, Generative AI}
	\resumeSubItem{Cloud \& Platforms}{AWS Lambda/S3, Groq, Lovable AI}
	\resumeSubItem{Soft Skills}{Problem Solving, Technical Writing, Public Speaking, Communication}
	\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Experience}
  \resumeCompanyHeading{TheHouseKraft}{Bangalore, India}
  {Machine Learning Engineer (Full-time)}{Dec 2024 - Present}
  \resumeItemListStart
  \resumeItem{Floor Plan Analysis}
    {Developed a comprehensive floor plan analysis system with 95\% accuracy using computer vision models for detecting rooms, walls, windows and furniture in architectural drawings.}
  \resumeItem{Automated Detection}
    {Built robust detection systems for architectural elements in floor plan images, enabling accurate identification of spatial relationships and structural components.}
  \resumeItem{Measurement Implementation}
    {Implemented measurement and visualization capabilities, generating detailed JSON analysis outputs for integration with downstream applications and client systems.}
  \resumeItem{Production Pipeline}
    {Designed and deployed reliable production pipeline using Python, Replicate, and Cog, ensuring consistent and scalable performance in real-world applications.}
  \resumeItem{AI Infrastructure}
    {Created scalable AI infrastructure for processing and analyzing architectural floor plans, enabling seamless handling of diverse input formats and complexities.}
  \resumeItem{Performance Optimization}
    {Optimized model performance and system architecture for production deployment, balancing computational requirements with accuracy demands.}
  \resumeItemListEnd
  
  \resumeCompanyHeading{Deduce Technologies}{Bangalore, India}
  {AI Developer (Full-time)}{May 2024 - Dec 2024}
  \resumeItemListStart
  \resumeItem{Automated Pipelines}
    {Engineered and deployed automated pipelines, resulting in a \textbf{30\% reduction in processing time} and significantly enhancing workflow efficiency across teams.}
  \resumeItem{Advanced AI Technologies}
    {Leveraged cutting-edge AI technologies, including LLMs, Transformers, OCRs, and NLP, to develop solutions that improved decision-making processes and drove business growth.}
  \resumeItem{End-to-End Pipelines}
    {Architected and implemented comprehensive end-to-end AI pipelines, achieving a \textbf{100\% compliance rate} with output quality standards and enhancing model reliability.}
  \resumeItem{Productivity Boost}
    {Drove organizational productivity by optimizing AI-driven processes, achieving a remarkable \textbf{250\% increase} in operational efficiency and throughput.}
  \resumeItem{Model Training}
    {Conducted training and \textbf{fine-tuning} of AI models using tailored custom datasets, leading to a \textbf{15\% improvement} in model accuracy and performance on resource-constrained hardware.}
  \resumeItem{Geospatial Data Analysis}
    {Utilized QGIS to analyze geospatial data, integrating advanced AI models to produce \textbf{highly accurate spatial analyses} and data visualizations that supported strategic decision-making.}
  \resumeItemListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{AI Web Researcher}{A Windows-optimized research assistant that leverages locally-run LLMs through Ollama to conduct thorough, automated online research. Breaks down queries into focused areas, performs systematic web searching and scraping, compiles findings into documented research, and provides comprehensive summaries with source attribution. \textbf{Tech Stack:} Python, Ollama, LangChain, BeautifulSoup, Windows Optimization.}
\vspace{5pt}
\resumeSubItem{LineScribe}{An AI Powered OCR integration with LLama-3.2 70b for accurate text detection using line segmentation, scene text recognition, and NLP segregation tasks. \textbf{Tech Stack:} Python, Groq, Llama, OpenCV, Transformers, Streamlit for UI.}
\vspace{5pt}
\resumeSubItem{Aura - Multilingual Transliteration}{A multilingual real-time transliteration system supporting major Indic languages including Hindi, Kannada, Bengali, and more. Features real-time processing, user-friendly interface, and customization options. \textbf{Tech Stack:} Python, NLP, Machine Learning, Streamlit.}
\vspace{5pt}
\resumeSubItem{Gradient Descent Visualization}{An interactive visualization tool for understanding gradient descent algorithm. Features multiple function selections, real-time updates of values, and dynamic controls for learning rate and iterations. \textbf{Tech Stack:} Python, Streamlit, Mathematical Visualization, Interactive Plotting.}
\resumeSubHeadingListEnd

\vspace{-5pt}
%-----------EDUCATION-----------------
\section{Education}
  \resumeCompanyHeading
    {K.N.S. Institute of Technology}{Bangalore, India}
    {Bachelor of Engineering - Mechanical Engineering;  GPA: 8.2}{July 2018 - June 2022}

\vspace{5pt}

\end{document} 